---
title: "The selector: Identifying the Most Appropriate Test Statistic For Assessing Model Fit"
author: "Njål Foldnes"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
citation_package: natbib
bibliography: bibsel.bib
biblio-style: apalike
---

---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The selector package uses bootstrapping to help select the best possible test statistic to 
evaluate a latent variable model. The procedure was proposed by @gronneberg2019testing, and a tutorial is given in @fold2. Basically, the sample is transformed so that it fits the model exactly, and bootstrap samples are drawn from the transformed sample. In each bootstrap sample the p-value of various test statistics are calculated. Finally, the test statistic whose empirical p-value distribution is closest to the uniform distribution is selected. The metric used to select the best statistic is chosen by the user, and have the following options :

* AD: Anderson-Darling distance to uniform. (Default)
* CVM: Cramer-Von Mises Test
* KS: Kolmogorov-Smirnov distance to uniform
* EC5: Type I error control closest to 5\%

The test statistics available as candidates are:

* ml: normal-theory maximum likelihood ratio test
* sb: satorra-bentler mean scaled test
* eba2: eba test with 2 blocks (see @fold1 for eigenvalue block-averaging tests)
* eba4: eba test with 4 blocks 
* ebaf: eba test with block size 1
* wl: the scaled F test of @wu2017approximations
* ss: scaled-and-shifted test of @asparouhov2010simple




## An example

The user first uses lavaan to fit the model to the sample, obtaining a fit object $f$.
The object may be used to calculate p-values for a variety of so-called robust test statistics.
```{r, message=F, warning=F}
library(psych)
library(dplyr)
library(lavaan)
library(selector)
                
#random subsample of big-five dataset
data(bfi)# from psych package
set.seed(1234)
my.sample <- sample_n(bfi, size=200)

#model with two factors
my.model <- "A =~ A1+A2+A3+A4+A5; O =~ O1+O2+O3+O4+O5"

#fit model
f <- sem(my.model, data=my.sample)

#let us calculate the p-values of the candidate test statistics
round(test_pvalues(f),3)
```

The *test_pvalues()* function calculates the p-value for the test of correct model specification for the above-mentioned statistics.
The ml test strongly suggests that the model is misspecified.
The sb test also suggests that the model is misspecified, but less so than the ml test.
The remaining tests suggest that we do not have strong evidence for model misspecification.


So which test is most trustworthy? The main function *selector(f)* runs the bootstrap (so it has considerable running time) and extracts the p-values for each of the statistics.

```{r, message=F, warning=F}
selector.result <- selector(f)
```

In this case, the eba2 p-values are closest to uniform in the Anderson-Darling metric.
Therefor, the researcher should place the most confidence in this statistic. The p-value histogram shows that eba2 has a rather uniform distribution of bootstrapped p-values. 


The selector returns an object containing the distance-to-uniform metrics for each of the metrics mentioned above

```{r}
selector.result$metrics
```
In terms of the first 3 metrics, the eba2 is the best performer. Howere, using metric EC5, 
it is outperformed by ebafull and wl. 

In addition, the p-value associated with the classical Bollen-Stine bootstrap approach, applied to each of the test statistics, is available:
```{r}
selector.result$bootstrap.pvals
```



## References


